Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-04-25 paper.tex
Added info for some methods in ALS phase

\todo{Revise intro to this section}
The experimental results have been obtained from four different approaches:
1. Applying ALS technique
2. Employing Bias as well as ALS technique
3. Using just Bias 
4. Results stemmed from ommiting the impact of predicted value of canstant files 
In all above approaches, dummy classifier which makes predictions using simple rules\cite{URL}has been used to indicate that how much predicted value would tend to be anticipate as the dominent value of the utility matrix. This classifier is considered as an accuracy evaluator since the binary utility matrix is consist of \{1,0\} which respectively represent whether a difference has been observed between the same files in two different conditions (by comapring their checksums) or not.
With the knowledge of the fact that Random Unreal method is not applicable into our case study we used its results as the comparision between the unrealistic method and realistics ones. In this regard, the aformentioned approaches are propossed and tried to lessen the gaps between the best results from random-unreal and the applied one.

\subsection{ALS without biases}

\todo{1. Use the same ordering and paragraph headings as in the method 
section. 2. Don't mix multiple ideas/results in the same paragraph. 3. 
Mention and describe the figure before discussing it.}
\subsubsection{Random Unreal}
Figure~\ref{fig:unreal method} represents
the accuracy graph of Complete Columns method with comparision to dummy
                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-5vs6-PFS}
                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-5vs7-PFS}
                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-6vs7-PFS}
        \caption{Average performance of Random Unreal methods in three different condition pairs}
        \label{fig:unreal method}

@@

Figure~\ref{fig:columns method} represents
the accuracy graph of Complete Columns method with comparision to dummy
                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-5vs6-PFS}
                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-5vs7-PFS}
                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-6vs7-PFS}
        \caption{Average performance of Complete Columns methods in three different condition pairs}
        \label{fig:columns method}

@@

@@

@@

Results show that in all condition pairs Complete Columns method has 
almost a constant accuracy even if the training ratio increased and it 
is almost two times less than dummy classifier in more differentiated 
condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the 
best case which it means in similar conditions the Complete Columns 
accuracy is as much accurate as the Dummy classifier which is $0.65$ 
percent Figure~\ref{fig:columns method} represents
the accuracy graph of Complete Columns method with comparision to dummy 
classifier over the increasement of the training ratio.\\

In general the accuracy pattern of the two Complete Rows and 
RS methods show similar decline and grow behavior over the 
training ratio axis however it can be subject to considerable 
fluctuations in differentiated condition pairs. Dispite of their 
likely irrational behaviour, they always have better accuracy 
for the training size with less than $0.3$ in comparison to other 
methods. This better performance (around 75 percent)is almost three 
times higher than other methods in condition pairs with more 
differences but just 20 percent better when the conditions are more 
similar to each other (CentOS5 vs CentOS6) with accuracy of $90\%$.
Figure~\ref{fig:RS_Rows} represents
the accuracy graph of these two methods with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_6vs7}
        \end{subfigure}
        \caption{Average performance of RS and Complete Rows methods in three different condition pairs}
        \label{fig:RS_RowS}
\end{figure}

>>>>

The experimental results have been obtained from four different approaches:
1. Applying ALS technique (ALS)
2. Employing Bias as well as ALS technique (ALS-Bias)
3. Using just Bias (Bias)
4. Results stemmed from ommiting the impact of predicted value of canstant files 
In all above approaches, dummy classifier which makes predictions using simple rules\cite{URL}has been used to indicate that how much predicted value would tend to be anticipate as the dominent value of the utility matrix. This classifier is considered as an accuracy evaluator since the binary utility matrix is consist of \{1,0\} which respectively represent whether a difference has been observed between the same files in two different conditions (by comapring their checksums) or not.
With the knowledge of the fact that Random Unreal method is not applicable into our case study we used its results as the comparision between the unrealistic method and realistics ones. In this regard, the aformentioned approaches are propossed and tried to lessen the gaps between the best results from random-unreal and the applied one.

\subsection{ALS without biases}
In this phase of the experiment, the Alternating Least Squares techniq of Collaborative Filtering is applied for all provided methods. \todo{should I talk about ALS in here?}
\subsubsection{Random Unreal}
Figure~\ref{fig:unreal method} represents
The accuracy graph of Random Unreal method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of Random Unreal methods in three different condition pairs}
        \label{fig:unreal method}
\end{figure}
This method has a great performance with absolute accouracy of more than $0.95$ even by accessing to small taining size of 10 percent. As it mentioned earlier this method is not applicable in pipline due to timestamp cosideration but it is a good criteria to estmiate the performance of other methods and try to modify the proposed methods in order to their accuracy be as colsed as possible to the Random Unreal method ones.

@@

Figure~\ref{fig:columns method} represents
the accuracy graph of Complete Columns method with comparision to dummy
classifier over the increasement of the training ratio.
As it can be seen Complete Columns method has
almost a constant accuracy even if the training ratio increased and it
is almost two times less than dummy classifier in more differentiated
condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the
best case which it means in similar conditions the Complete Columns
accuracy is as much accurate as the Dummy classifier which is $0.65$
percent.

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of Complete Columns methods in three different condition pairs}
        \label{fig:columns method}
\end{figure}

@@

As it can be observed, This method has some flactuation over the gowth of training set size. These falactuations are more frequent in condition pairs which have higher difference positive ratio. Also by enlarging the training ratio specially between $0.3$ to $0.7$, we can see dummy classifier has better results than Complete Rows ones. In other words despite of better performance of Complete Rows than dummy classifier at the last 10 percent of the graph, its accuracies are less than dummy classifiers ones.  

@@

Same to the Complete Row method, RS method has some flactuation but not as frequent as Complete Rows method. Althogh there are some up and down trends specialy with training ratio range of $0.2$ to $0.6$ but its constant growth trend after training ratio $0.3$ in condition pairs with high difference positive ratio is considerable. The method can be $0.99$ percent accurate when it has over 70 percent of the data however this accuracy can be achived with higher training ratio (over 80 percent) for C5C6.  

@@

In general the accuracy pattern of the two Complete Rows and 
RS methods show similar decline and grow behavior over the 
training ratio axis however it can be subject to considerable 
fluctuations in differentiated condition pairs. Dispite of their 
likely irrational behaviour, they always have better accuracy 
for the training size with less than $0.3$ in comparison to other 
methods. This better performance (around 75 percent)is almost three 
times higher than other methods in condition pairs with more 
differences but just 20 percent better when the conditions are more 
similar to each other (CentOS5 vs CentOS6) with accuracy of $90\%$.
Figure~\ref{fig:RS_Rows} represents
the accuracy graph of these two methods with comparision to dummy
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs6}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs7}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_6vs7}
        \caption{Average performance of RS and Complete Rows methods in three different condition pairs}
        \label{fig:RS_RowS}
